%-------------------------
% Resume in Latex
% Author: Suyash Deo
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Suyash Deo} \\ \vspace{4pt}
    \textbf{\Large \scshape MSc Computer Science Student} \\ \vspace{4pt}
    \small \faPhone\ +91-7378826927 ~ 
    \href{mailto:suyashdeo122@gmail.com}{\faEnvelope\ \underline{suyashdeo122@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/suyash-deo-269a453a1}{\faLinkedin\ \underline{linkedin.com/in/suyashdeo}} 
\end{center}


%-----------SUMMARY-----------
\section{Summary}
Computer Science student with hands-on experience in full-stack development and modern web technologies. Skilled in JavaScript, Node.js, PHP, Firebase, MySQL, PostgreSQL, and MongoDB. Passionate about backend development, software engineering, and building scalable applications with strong problem-solving and teamwork skills.



%-----------SKILLS-----------
\section{Skills}
\textbf{Programming \& Querying:} SQL, Python, PHP, JavaScript, Java  \\
\textbf{Web Technologies:} HTML, CSS, React.js, Node.js, Express.js, Bootstrap \\
\textbf{Database \& Backend Services :} MySQL, PostgreSQL, MongoDB, Firebase, Convex \\
\textbf{Tools \& Platforms:} Git, GitHub, VS Code, Postman  \\
\textbf{Concepts:} Full-Stack Development, REST APIs, Database Management, Problem Solving   \\


%---------------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{DES Pune University}{Pune, Maharashtra}
{Master of Science (M.Sc.) in Computer Science}{\textbf{2026 -- Present}}

\resumeSubheading
{Marathwada Mitra Mandal's College of Commerce}{Pune, Maharashtra}
{Bachelor of Science (B.Sc.) in Computer Science $|$ CGPA: 7.77 $|$ Grade: A}{\textbf{2022 -- 2025}}

\resumeSubHeadingListEnd

%---------------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Web Development Intern}{\textbf{May 2026 -- June 2026}}
{\normalfont CodSoft (Virtual Internship)}{\normalfont Remote}
\resumeItemListStart

\resumeItem{Worked on web development tasks and projects as part of a 1-month virtual internship program.}

\resumeItem{Developed responsive web pages using HTML, CSS, JavaScript, and modern development practices.}

\resumeItem{Improved frontend development, debugging, and problem-solving skills through hands-on project work.}

\resumeItem{Collaborated on assigned tasks while gaining practical exposure to software development workflows and version control.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%---------------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{TrainerOS} $|$ \emph{React Native, Firebase, Node.js, MongoDB}}{\textbf{Feb 2026 - Present}}
\resumeItemListStart

\resumeItem{Developing a fitness trainer-client management platform with workout tracking, progress monitoring, and authentication features.}

\resumeItem{Built responsive frontend screens and integrated backend services for real-time data management.}

\resumeItem{Designed scalable database structures and implemented user-friendly UI/UX features.}

\resumeItem{Worked on API integration, authentication, and application performance improvement.}

\resumeItemListEnd

\resumeProjectHeading
{\textbf{TripTales} $|$ \emph{PHP, PostgreSQL, HTML, CSS, JavaScript}}{\textbf{2025}}

\resumeItemListStart

\resumeItem{Built a travel-based web application for exploring destinations and managing travel-related content.}

\resumeItem{Developed responsive frontend interfaces and backend functionalities using PHP and PostgreSQL.}

\resumeItem{Implemented authentication modules, CRUD operations, and dynamic content rendering.}

\resumeItem{Improved database management and backend logic handling through practical development experience.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%---------------CERTIFICATIONS & ACHIEVEMENTS-----------------
\section{Certifications \& Achievements}
\resumeSubHeadingListStart

\resumeItem{\textbf{Research Paper Presentation:} Presented a research paper on nature-inspired optimization algorithms for the Travelling Salesman Problem (TSP) at ICAISS-2026.}

\resumeItem{\textbf{Virtual Internship:} Completed Web Development Virtual Internship at CodSoft.}

\resumeItem{\textbf{AWS Machine Learning Course:} Completed coursework covering supervised learning, forecasting, SageMaker, and machine learning fundamentals.}

\resumeSubHeadingListEnd


\end{document}
